---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RepPack27

<!-- badges: start -->
<!-- badges: end -->

The goal of RepPack27 is to be able to apply a simple between-subjects ANOVA (two-way) simply by using the 
ANOVA2_BW() function. The following will show an example using the 'RTDATA' built in dataset.

## Installation

You can install the development version of RepPack27 like so:

``` r
# This is how you can install the package:

remotes::install_github("brittn27/RepPack27")

```

## Example

This is a basic example which shows you how to solve a common problem:

```{r load data}
data(RTDATA)
summary(RTDATA)
Data <- RTDATA

```

```{r example}
library(RepPack27)
## basic example code  of summary --

?ANOVA2_BW()

x <- RTDATA$difficulty
y <- RTDATA$depth
z <- RTDATA$RT
#Data <- RTDATA
summary(Data)

```

```{r ANOVA output}
# and then an ANOVA
ANOVA2_BW(x,y,z)
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(RT~difficulty,Data)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
